---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dfdetective

Column names are sometimes opaque. And sometimes there are hundreds of them. The goal of `dfdetective` is to scour data frames when you have only a vague idea what you're looking for. The functions are mostly thin wrappers around combinations of `lapply()...unique()...grep()`.

## Installation

You can install the released version of dfdetective from GitHub via:

``` r
remotes::install_github("daranzolin/dfdetective")
```

### Example A: You want to search all rows to match a pattern.

```{r warning=FALSE, message=FALSE}
library(dfdetective)
library(fivethirtyeight)
library(dplyr)

find_unique_vals(antiquities_act, "chaco")

agencies <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-01-15/agencies.csv")
find_unique_vals(agencies, "^B$")
```

### Example B: You want to find columns with n unique variables

This is especially useful when searching for binary variables.

```{r}
find_n_unique_vals(comic_characters, 2:4) # You can pass a numeric vector to the n_unique argument
```

### Example C: You know the column names and you want to check the unique values

```{r}
get_unique_vals(san_andreas, contains("worry")) #you can pass classic dplyr select helpers, e.g. starts_with(), contains(), etc.
```
